Supplementary Content for the article *The role of functional diversity in ecosystem regime shifts*

### 2022-03-31 experiments/2_supplement/supplement.Rmd
Update Supplement

```{r sb-div-effect4, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect4)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_highvar1 <- readRDS(here("data", "2_supplement", "puzzle1_2.RDS"))
plot_dynamics(sim_res_highvar1)
#ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)
```

>>>>

```{r sb-div-effect4, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect4)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_highvar1 <- readRDS(here("data", "2_supplement", "puzzle1_2.RDS"))

p <- plot_dynamics(sim_res_highvar1)
p[[1]] <- p[[1]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[2]] <- p[[2]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[3]] <- p[[3]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[4]] <- p[[4]] + 
  xlab("time(h)") + 
  ylab(expression(log[10](concentration)(µM))) + 
  labs(colour = "substrate")

p

#ggsave(here("simulations", "expt2", "figures", "switching_novar.pdf"), width = 10)
```
